\Large \bf Byteboy : A Byteman Companion application

### 2017-12-08 final-paper/paper.la_.tex
fix(paper): fixed reference formatting so the cite numbers appear in generated pdf

\bibitem{bytemanguide}
Byteman Programmer's Guide, 3.0.10, Apr 27, 2017
\\\texttt{http://downloads.jboss.org/byteman
/3.0.10/ProgrammersGuide.html}

\bibitem{bytemanblog}
Dinn, Andrew. (2011). A Byteman Tutorial. \\\textit{JBoss Developer}. Retrieved from: 
\\\texttt{https://developer.jboss.org/wiki
/ABytemanTutorial}

@@

\bibitem{yocode}
Yo Code - Extension Generator
\\\texttt{https://code.visualstudio.com/docs
/extensions/yocode}

\bibitem{bytemanextension}
Byteman Language Extension.
\\\texttt{https://github.com/aptmac/byteboy
/tree/master/byteman-language-extension}

\bibitem{textmate}
Textmate: Language Grammars
\\\texttt{https://manual.macromates.com/en
/language\_grammars}

@@

\bibitem{hprof}
HPROF: A Heap/CPU Profiling Tool
\\\texttt{https://docs.oracle.com/javase/7/docs/technotes
/samples/hprof.html}

\bibitem{javap}
javap - The Java Class File Disassembler
\\\texttt{https://docs.oracle.com/javase/7/docs/technotes
/tools/windows/javap.html}

>>>>

\bibitem{bytemanguide}
Byteman Programmer's Guide, 3.0.10, Apr 27, 2017
\\\texttt{http://downloads.jboss.org/byteman/\newline3.0.10/ProgrammersGuide.html}

\bibitem{bytemanblog}
Dinn, Andrew. (2011). A Byteman Tutorial. 
\\\textit{JBoss Developer}. Retrieved from: \\\texttt{https://developer.jboss.org/wiki/\newline ABytemanTutorial}

@@

\bibitem{yocode}
Yo Code - Extension Generator
\\\texttt{https://code.visualstudio.com/docs/\newline extensions/yocode}

\bibitem{bytemanextension}
Byteman Language Extension.
\\\texttt{https://github.com/aptmac/byteboy/tree/\newline master/byteman-language-extension}

\bibitem{textmate}
Textmate: Language Grammars
\\\texttt{https://manual.macromates.com/en/\newline language\_grammars}

@@

\bibitem{hprof}
HPROF: A Heap/CPU Profiling Tool
\\\texttt{https://docs.oracle.com/javase/7/\newline docs/technotes/samples/hprof.html}

\bibitem{javap}
javap - The Java Class File Disassembler
\\\texttt{https://docs.oracle.com/javase/7/\newline docs/technotes/tools/windows/javap.html}
